\vspace{-2.5em} Spatio-angular transfer functions for fluorescence microscopes\vspace{-1em}

### 2018-04-18 notes/2018-02-23-spatio-angular-kernel/report/report.tex
y-oriented -> z-oriented typo
Fixed small normalization issues.

\begin{figure}[h]
 \captionsetup{width=1.0\linewidth}
 \centering
   \centering
   \includegraphics[width = 1.\textwidth]{../calculations/compare-ft/psfs.pdf}
   \caption{\textbf{Left:} Point spread functions and \textbf{Right:} optical
     transfer functions for a single-view fluorescence microscope with
     $\text{NA}=0.8$ and $n_o=1.33$ under the paraxial approximation.
     \textbf{Black:} $l=0, m=0$ spherical harmonic---an isotropic distribution
     of fluorophores. \textcolor{blue}{\textbf{Blue:}} $l=2, m=0$ spherical
     harmonic---negative fluorophores near the transverse plane, positive
     fluorophores near the optical axis. \textcolor{red}{\textbf{Red:}}
     $x$-oriented dipole. \textcolor{OliveGreen}{\textbf{Green:}} $y$-oriented
     dipole.}
   \label{fig:para}
\end{figure}

@@

   \caption{Geometric construction for evaluating $A^{(p)}(\bs{\nu})$ and
     $B^{(p)}(\bs{\nu})$. We need to find the boundaries of integration for the
     overlapping region of two circles with radius $\nu_o$ and distance $\nu$
     between their centers. The region is given by four times the difference in
     area between a sector of angle $\arccos\left(\frac{\nu}{2\nu_o}\right)$ and
     a triangle with base $\nu/2$ and hypotenuse $\nu_o$.}

@@

  \mathcal{F}_2\left\{{b^{(p)}}(r_d')\cos(\phi_d')\right\} = i\me^{i\phi_\nu}\mathcal{H}_{-1}\{{b^{(p)}}(r_d')\} - i\me^{-i\phi_\nu}\mathcal{H}_{1}\{{b^{(p)}}(r_d')\}.

@@

  \mathcal{F}_2\left\{{b^{(p)}}(r_d')\cos(\phi_d')\right\} = \frac{i\cos\phi_\nu}{2}\mathcal{H}_{1}\{{b^{(p)}}(r_d')\}.

@@

  \mathcal{F}_2\left\{{b^{(p)}}(r_d')\cos(\phi_d')\right\} = \left(\frac{\text{NA}}{n_o}\right)\frac{i\nu\cos\phi_\nu}{\nu_o^2}\, \Pi\left(\frac{\nu}{\nu_o}\right) = \left(\frac{\text{NA}}{n_o}\right)\frac{i\nu_x}{\nu_o^2}\, \Pi\left(\frac{\nu}{\nu_o}\right).

@@

  \mathcal{F}_2\left\{{b^{(p)}}(r_d')\sin(\phi_d')\right\} = \left(\frac{\text{NA}}{n_o}\right)\frac{i\nu\sin\phi_\nu}{\nu_o^2}\, \Pi\left(\frac{\nu}{\nu_o}\right) = \left(\frac{\text{NA}}{n_o}\right)\frac{i\nu_y}{\nu_o^2}\, \Pi\left(\frac{\nu}{\nu_o}\right).  

@@

    \mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\right\} &= -\left(\frac{\text{NA}}{n_o}\right)^2\frac{1}{\nu_0^4}\left\{\left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2 \left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right]\right\} - \left(\frac{\text{NA}}{n_o}\right)^2\frac{1}{\nu_0^4}\left\{\left[\nu_y\, \Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2 \left[\nu_y\, \Pi\left(\frac{\nu}{\nu_o}\right)\right]\right\}.\label{eq:auto}

@@

    \mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\right\} &= -\left(\frac{\text{NA}}{n_o}\right)^2\frac{1}{\nu_0^4}\left\{\left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2^x \left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right]\right\} - \left(\frac{\text{NA}}{n_o}\right)^2\frac{1}{\nu_0^4}\left\{\left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2^y \left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right]\right\}.

@@

  &\frac{-1}{\nu_0^4}\left\{\left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2^x \left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right]\right\} = \\
  &=  \frac{-4}{\nu_o^4}\Bigg[\int\limits_0^{\nu_o} d\tau\, \tau \int\limits_0^{\arccos\left(\frac{\nu}{2\nu_o}\right)}d\phi_{\tau}(-\tau^2\cos^2\phi_{\tau} + \nu\tau\cos\phi_{\tau}) - \int\limits_0^{\nu/2}d\tau_x \int\limits_0^{\tau_x \frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}}d\tau_y(-\tau_x^2 + \nu\tau_x)\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right).

@@

  &=\frac{-4}{\nu_o^4}\Bigg[\int\limits_0^{\nu_o} d\tau\, \frac{-\tau^3}{2}\left(\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \arccos\left(\frac{\nu}{2a}\right)\right) + \nu\tau^2\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)}\nonumber \\ &\hspace{5em}- \int\limits_0^{\nu/2}d\tau_x \left(-\tau_x^3 + \nu\tau_x^2\right)\frac{2 \nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
  &=  \frac{-4}{\nu_o^4}\Bigg[\frac{-\nu_o^4}{8}\left(\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \arccos\left(\frac{\nu}{2\nu_o}\right) \right) + \frac{2\nu_o^4}{3}\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)}\nonumber \\ &\hspace{5em} - \frac{5\nu^2\nu_o^2}{48}\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
  &=  \frac{1}{2}\Bigg[\left(\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \arccos\left(\frac{\nu}{2\nu_o}\right) \right) - \frac{16}{3}\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)}\nonumber \\ &\hspace{5em} + \frac{5\nu^2}{6\nu_o^2}\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
  &= \frac{1}{2}\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \left(\frac{13}{3} - \frac{5\nu^2}{6\nu_o^2}\right)\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
  &= \left[\frac{1}{2}\arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{1}{6}\left[13 - 10\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right).\label{eq:auto1}

@@

  &\frac{-1}{\nu_0^4}\left\{\left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2^y \left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right]\right\} = \\
  &=  \frac{-4}{\nu_o^4}\Bigg[\int\limits_0^{\nu_o} d\tau\, \tau \int\limits_0^{\arccos\left(\frac{\nu}{2\nu_o}\right)}d\phi_{\tau}(-\tau^2\sin^2\phi_{\tau}) - \int\limits_0^{\nu/2}d\tau_x \int\limits_0^{\tau_x \frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}}d\tau_y(-\tau_y^2)\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right).

@@

  &=\frac{-4}{\nu_o^4}\Bigg[\int\limits_0^{\nu_o} d\tau\, \frac{-\tau^3}{2}\left(\frac{-\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \arccos\left(\frac{\nu}{2a}\right)\right) - \int\limits_0^{\nu/2}d\tau_x \frac{-\tau_x^3}{3}\left(\frac{2 \nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right)^3\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
  &=  \frac{-4}{\nu_o^4}\Bigg[\frac{-\nu_o^4}{8}\left(\frac{-\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \arccos\left(\frac{\nu}{2\nu_o}\right) \right) + \frac{\nu_o^4}{12}\frac{\nu}{2\nu_o}\sqrt[3]{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
  &=  \Bigg[\frac{1}{2}\arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{1}{2}\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} - \frac{1}{3}\frac{\nu}{2\nu_o}\sqrt[3]{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right). \label{eq:auto2}

@@

  \mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\right\} &= \left(\frac{\text{NA}}{n_o}\right)^2\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{1}{3}\left[8 - 5\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} - \frac{1}{3}\frac{\nu}{2\nu_o}\sqrt[3]{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
    \mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\right\} &= \left(\frac{\text{NA}}{n_o}\right)^2\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \left[3 - 2\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right).

>>>>

\begin{figure}[h]
 \captionsetup{width=1.0\linewidth}
 \centering
   \centering
   \includegraphics[width = 1.\textwidth]{../calculations/compare-ft/psfs.pdf}
   \caption{\textbf{Left:} Point spread functions and \textbf{Right:} optical
     transfer functions for a single-view fluorescence microscope with
     $\text{NA}=0.8$ and $n_o=1.33$ under the paraxial approximation.
     \textbf{Black:} $l=0, m=0$ spherical harmonic---an isotropic distribution
     of fluorophores. \textcolor{blue}{\textbf{Blue:}} $l=2, m=0$ spherical
     harmonic---negative fluorophores near the transverse plane, positive
     fluorophores near the optical axis. \textcolor{red}{\textbf{Red:}}
     $x$-oriented dipole. \textcolor{OliveGreen}{\textbf{Green:}} $z$-oriented
     dipole.}
   \label{fig:para}
\end{figure}

@@

   \caption{Geometric construction for evaluating the autocorrelations. We need
     to integrate over the overlapping region of two circles with radius $\nu_o$
     and distance $\nu$ between their centers. The region is given by four times
     the difference in area between a sector of angle
     $\arccos\left(\frac{\nu}{2\nu_o}\right)$ and a triangle with base $\nu/2$
     and hypotenuse $\nu_o$.}

@@

  \mathcal{F}_2\left\{{b^{(p)}}(r_d')\cos(\phi_d')\right\} = \frac{1}{2}\left[i\me^{i\phi_\nu}\mathcal{H}_{-1}\{{b^{(p)}}(r_d')\} - i\me^{-i\phi_\nu}\mathcal{H}_{1}\{{b^{(p)}}(r_d')\}\right].

@@

  \mathcal{F}_2\left\{{b^{(p)}}(r_d')\cos(\phi_d')\right\} = -i\cos\phi_\nu \mathcal{H}_{1}\{{b^{(p)}}(r_d')\}.

@@

  \mathcal{F}_2\left\{{b^{(p)}}(r_d')\cos(\phi_d')\right\} = -\left(\frac{\text{NA}}{n_o}\right)\frac{2i\nu\cos\phi_\nu}{\nu_o^2}\, \Pi\left(\frac{\nu}{\nu_o}\right) = -\left(\frac{\text{NA}}{n_o}\right)\frac{2i\nu_x}{\nu_o^2}\, \Pi\left(\frac{\nu}{\nu_o}\right).

@@

  \mathcal{F}_2\left\{{b^{(p)}}(r_d')\sin(\phi_d')\right\} = -\left(\frac{\text{NA}}{n_o}\right)\frac{2i\nu\sin\phi_\nu}{\nu_o^2}\, \Pi\left(\frac{\nu}{\nu_o}\right) = -\left(\frac{\text{NA}}{n_o}\right)\frac{2i\nu_y}{\nu_o^2}\, \Pi\left(\frac{\nu}{\nu_o}\right).  

@@

    \mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\right\} &= -\left(\frac{\text{NA}}{n_o}\right)^2\frac{4}{\nu_0^4}\left\{\left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2 \left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right]\right\} - \left(\frac{\text{NA}}{n_o}\right)^2\frac{4}{\nu_0^4}\left\{\left[\nu_y\, \Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2 \left[\nu_y\, \Pi\left(\frac{\nu}{\nu_o}\right)\right]\right\}.\label{eq:auto}

@@

    \mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\right\} &= -\left(\frac{\text{NA}}{n_o}\right)^2\frac{4}{\nu_0^4}\left\{\left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2^x \left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right]\right\} - \left(\frac{\text{NA}}{n_o}\right)^2\frac{4}{\nu_0^4}\left\{\left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2^y \left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right]\right\}.

@@

  &\frac{-4}{\nu_0^4}\left\{\left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2^x \left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right]\right\} = \\
  &=  \frac{-16}{\nu_o^4}\Bigg[\int\limits_0^{\nu_o} d\tau\, \tau \int\limits_0^{\arccos\left(\frac{\nu}{2\nu_o}\right)}d\phi_{\tau}(-\tau^2\cos^2\phi_{\tau} + \nu\tau\cos\phi_{\tau}) - \int\limits_0^{\nu/2}d\tau_x \int\limits_0^{\tau_x \frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}}d\tau_y(-\tau_x^2 + \nu\tau_x)\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right).

@@

  &=\frac{-16}{\nu_o^4}\Bigg[\int\limits_0^{\nu_o} d\tau\, \frac{-\tau^3}{2}\left(\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \arccos\left(\frac{\nu}{2a}\right)\right) + \nu\tau^2\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)}\nonumber \\ &\hspace{5em}- \int\limits_0^{\nu/2}d\tau_x \left(-\tau_x^3 + \nu\tau_x^2\right)\frac{2 \nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
  &=  \frac{-16}{\nu_o^4}\Bigg[\frac{-\nu_o^4}{8}\left(\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \arccos\left(\frac{\nu}{2\nu_o}\right) \right) + \frac{2\nu_o^4}{3}\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)}\nonumber \\ &\hspace{5em} - \frac{5\nu^2\nu_o^2}{48}\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
  &=  2\Bigg[\left(\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \arccos\left(\frac{\nu}{2\nu_o}\right) \right) - \frac{16}{3}\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)}\nonumber \\ &\hspace{5em} + \frac{5\nu^2}{6\nu_o^2}\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
  &= 2\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \left(\frac{13}{3} - \frac{5\nu^2}{6\nu_o^2}\right)\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
  &= \left[2\arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{2}{3}\left[13 - 10\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right).\label{eq:auto1}

@@

  &\frac{-4}{\nu_0^4}\left\{\left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right] \star_2^y \left[\nu_x\, \Pi\left(\frac{\nu}{\nu_o}\right)\right]\right\} = \\
  &=  \frac{-16}{\nu_o^4}\Bigg[\int\limits_0^{\nu_o} d\tau\, \tau \int\limits_0^{\arccos\left(\frac{\nu}{2\nu_o}\right)}d\phi_{\tau}(-\tau^2\sin^2\phi_{\tau}) - \int\limits_0^{\nu/2}d\tau_x \int\limits_0^{\tau_x \frac{2\nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}}d\tau_y(-\tau_y^2)\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right).

@@

  &=\frac{-16}{\nu_o^4}\Bigg[\int\limits_0^{\nu_o} d\tau\, \frac{-\tau^3}{2}\left(\frac{-\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \arccos\left(\frac{\nu}{2a}\right)\right) - \int\limits_0^{\nu/2}d\tau_x \frac{-\tau_x^3}{3}\left(\frac{2 \nu_o}{\nu}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right)^3\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
  &=  \frac{-16}{\nu_o^4}\Bigg[\frac{-\nu_o^4}{8}\left(\frac{-\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} + \arccos\left(\frac{\nu}{2\nu_o}\right) \right) + \frac{\nu_o^4}{12}\frac{\nu}{2\nu_o}\sqrt[3]{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
  &=  \Bigg[2\arccos\left(\frac{\nu}{2\nu_o}\right) - 2\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} - \frac{4}{3}\frac{\nu}{2\nu_o}\sqrt[3]{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\Bigg]\Pi\left(\frac{\nu}{2\nu_o}\right). \label{eq:auto2}

@@

  \mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\right\} &= 4\left(\frac{\text{NA}}{n_o}\right)^2\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{1}{3}\left[8 - 5\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2} - \frac{1}{3}\frac{\nu}{2\nu_o}\sqrt[3]{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
    \mathcal{F}_2\left\{{b^{(p)}}^2(r_d')\right\} &= 4\left(\frac{\text{NA}}{n_o}\right)^2\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \left[3 - 2\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right).
